---
title: "Getting a Gig"
author: "Sean Corcoran, Sarah Dodamead, Christopher Matos, Ethan Tenison"
date: "3/9/2020"
output: html_document
---

```{r libraries, message=FALSE, warning=FALSE}
list.of.packages <-
        c(
                "tidyverse",
                "googledrive",
                "janitor",
                "dplyr",
                "caret"
                
                
           )
#new.packages <-list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])]
library(googledrive)
library(tidyverse)
library(janitor)
library(dplyr)
library(caret)
```

## Pulling in the data 

```{r data, cache = TRUE}
 drive_download(as_id("1S4B1Txs-ycsyO0X6DEA5C1STHt1fXeOK"), overwrite = TRUE)
 data <- read.csv("EER396_Data_Set.csv", stringsAsFactors = FALSE)
 data <- clean_names(data)
 #str(data)
```


## Data Cleaning 

Everything before submitting profile has been removed. Even after profile submission, leads that have not provided their age have also been removed.

#### Variables that have been removed: 
-da_activated
-background_submit_Date
-submit_profile_time, data before this point is insufficient 
-orientation_selection_time
-orientation_start_time (we need to check to see if this is valueable)
-waitlist_end_date  (this would be more helpful if we knew what date they were put on a waitlist)
-mvr_initiated  
-mvr_cleared 
-criminal_initiated
-criminal_cleared
-dropship_kit_ordered
-orient_date
-start_date  this is connected to activation which we also deleted 
-first_dash_date, this is removed after the converted variable is created 
-planned_time 
-apply_date (this value is important if we need to calculate new day variables)
-applied_submarket
-planned_sp
-planned_sm 
-offer_end
-is_waitlist, all the waitlisted leads were removed before removing the variable.
-current_wl_status 
-dash_day, was removed because we use first_dash_day
-NA's were removed from submit_profile_time because we don't have enough data on individuals who haven't made it past that step.
-da_bgc_info_sub, removed because everything NA
-x, just an indentifier that I think believe has any meaning
-dash_applicant_id, just an indentifier that I think believe has any meaning
-dasher_id, just an indentifier that I think believe has any meaning
-zipcode, it has non US zip codes, so I just took it out. 

#### Variables that have been created: 
-converted, binary variable describing if a lead has converted or not


### Variables that have been imputed: 
-phone model, blanks set to unknown
-phone os, blanks set to unknown
-app_version, blanks set to unknown
-w9_signed, set to no 
-orientation_type, set to none if blank 
-offer, blanks set to none 
-offer_amt, NA's set to zero
-offer_deliv_req, NA's set to zero
-delivs, NA's set to zero


```{r datacleaning}
#Leads that converted are given a 1 in the converted column 
df <- data %>% mutate(converted = ifelse(!is.na(data$first_dash_date) & data$da_first_dash <=45, 1, 0)) %>% 
        filter(!is.na(submit_profile_time)) %>% 
        filter(is_waitlist != "waitlist") %>% 
        filter(!is.na(age)) %>% 
        select(-c("da_activated", "background_submit_date", "submit_profile_time", "orientation_selection_time","orientation_start_time", "mvr_initiated","mvr_cleared","criminal_initiated","criminal_cleared", "orient_date", "start_date", "first_dash_date", "planned_time", "waitlist_end_date" ,"dropship_kit_ordered","apply_date","planned_sp", "planned_sm", "offer_end", "is_waitlist", "current_wl_status","dash_day","da_bgc_info_sub", "x", "dasher_applicant_id", "dasher_id", "zip_code" ))
# Filling in blank data 
df$phone_model[df$phone_model == ''] <- "unknown"
df$phone_os[df$phone_os == ''] <- "unknown"
df$app_version[df$app_version == ''] <- "unknown"
df$offer[df$offer == ''] <- "blank"
df$w9_signed[df$w9_signed == ''] <- "no"
df$orientation_type[df$orientation_type == ''] <- "none"
df$offer_amt[is.na(df$offer_amt)] <- 0
df$offer_deliv_req[is.na(df$offer_deliv_req)] <- 0
df$delivs[is.na(df$delivs)] <- 0
        
 str(df)      
        
```


## Logistic Regression

```{r logistic_regression}
# da_mvr_bgc_start + da_mvr_bgc_pass +
logit <- glm(converted ~ age + orientation_type + channel + da_profile_submit + da_orientation_select
             + da_dropshipping_created + da_oriented + holdout + applied_submarket, data = df, family = "binomial")
summary(logit)
```
```{r linear regression with relavent variables at each step in application process}



```


